Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-05-04 hazelnut-popl17.tex
added TODO to cite polymorphic blocks paper

\maketitle
\begin{abstract}
Well-typed expressions are meaningful inductive structures, but programmers typically construct and manipulate them indirectly, as text that must pass through a parser and typechecker. Not all text survives this journey. In particular, text that arises transiently during the editing process, or when the programmer has made a mistake, is often malformed or ill-typed. Contending with (i.e. reasoning about) malformed text or well-formed but meaningless expressions is a difficult task, for programmers and their tools alike.

@@

>>>>

\maketitle
\begin{abstract}
Well-typed expressions are rich inductive structures, but programmers typically construct and manipulate them only indirectly, as text that must pass through a parser and typechecker. Not all text survives this journey. In particular, text that arises transiently during the editing process, or when the programmer has made a mistake, is often malformed or ill-typed. Contending with (i.e. reasoning about) malformed text or well-formed but meaningless expressions is a difficult task, for programmers and their tools alike.

@@

TODO: cite http://cseweb.ucsd.edu/~lerner/pb.html
